---
title: "Final_Project"
author: "Ahmed Farah"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#H0:My average daily screen time is less than or equal 2.
#Ha:My average daily screen time exceeds the 2 hours recommended time.

#Experts say adults should limit screen time to 2 hours. In this case, i will be using recommended limit time of 2 hours.

$H0: p = 2.0$ $Ha:p > 2.0$

```{r}
library(tidyverse)
library(ggplot2)
library(plotly)
```

```{r}
library(readxl)
ScreenTime <- read_excel("Documents/Data Science/ScreenTime.xlsx")
graph1 <- ggplot(ScreenTime, aes(x=Day, y=ScreenTime))+geom_line() + geom_point()+ labs(title = "Daily Screen Time Over Two Weeks", x="Day", y="Screen Time (hours)")

ggplotly(graph1)
```

#Each point on the line shows the screen time for a specific day

#Histogram of screen time disribution


```{r}
graph2 <- ggplot(ScreenTime, aes(x=ScreenTime))+geom_histogram(binwidth = 0.5, fill="skyblue", color="black")+labs(title = "Distribution of Daily Scrreen Time", x="Screen Time (hours)", y="Frequency")

ggplotly(graph2)
```
#The histogram will show the disribution of daily screentime, with each bar representing the frequency of screen time within  a certain range of hours.

#boxplot

```{r}
graph3 <- ggplot(ScreenTime, aes(y = ScreenTime)) + geom_boxplot(fill="lightgreen", color="black")+ labs("Boxplot of Daily Screen Time", y="Screen Time (Hours)")

ggplotly(graph3)

```
#no outliers for the Screen time data. Screen time is between 2.5 - 6.5

One-sample t-test
```{r}
t.test(ScreenTime$ScreenTime, mu=2, alternative = "greater")
```
# We reject the null hypothesis because the average daily screen is signifacnly greater than the 2 hour limit suggested for screen time.


#Two-sample t-test
#H0:There is no significant difference between the average screen time on weekends and weekdays.

#HA: The average screen time on weekends differs from weekdays.

$H0: weekends = weekdays$ $Ha: weekends \ne weekdays$
```{r}
weekdays <- ScreenTime %>% filter(Day %in% c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday"))

weekends <- ScreenTime %>% filter(Day %in% c("Saturday", "Sunday"))

t.test(weekends$ScreenTime, weekdays$ScreenTime, alternative = "two.sided")
```
#With a p-value = 0.67 we fail to reject the null hypothesis. This proves that there is insuffienct evidence to support that average screen time on weekends differs significantly from weekdays.
